Gender Dynamics in Academia: Analyzing Regrade Requests and Course Load Trends, 2010-2016

### 2024-02-14 outputs/paper/paper.qmd
finalize formatting

---
title: "The Relationship Between Gender Identities and Regrades among Undergraduate Students, 2010-2016"
subtitle: "A replication of Li and Zahar;"
author: Faiza Imam, Quang Mai & Catherine Punnoose 
thanks: "Code and data are available at: https://github.com/ponolite/gender_grade.git, DOI: 10.1257/pol.20210053"
date: today
date-format: long
abstract: "Academia is a complex ecosystem that feeds off a network of social, cultural and innovative influences which often, stem beyond societal norms. This paper replicates the gender implications regarding results in college students and explores potential fluctuations in request patterns over a semester by specifically analyzing the number of classes taken by students and their willingness to submit a grade request throughout the semester. Our results show that there is a trend for female students to submit regrade requests while taking fewer courses compared to a higher course load. Female students experienced grade increases (3%) compared to their male counterparts. We call for further investigation around this topic to understand gender disparities within the world of academia. "
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

Suceedingly, @fig-RegradeByClass shows the averaged distribution of the number of classes in which students are considered for regrades by gender. Observable in the graph, there is only data available on students who considered regrades in ‘0 class’ to ‘5 classes or more’ (CITE). Therefore, with the number of classes limited to 5, it’s more than likely that surveys understate the regraded data (CITE). Observably, with no or 0 classes, the majority of students didn’t consider regrade requests, with females upholding 41.2 % while males upholding 39.3%, making it a 1.9% difference. This trend of females considering for regrades is higher than males when the class number is lower, where at 1 class, a whopping 30.4% of females are considered for regrades in contrast to a meagre 22.7% of males. This translates to a huge margin of 7.7% between the two genders. However, as the number of classes extended above 1, or from 2 to 5 or more classes, more males considered asking for a regrade. For instance, at 3 classes, 8.9% of males considered for regrades as opposed to 7.1% of females; at 4 classes, 3.3% of males considered for regrades compared to 2% of females and finally, at 5 classes or more, a great 5.2% of males considered for regrades compared to a small 2.1% females. Statistically then, while the difference is negligible in some categories of class number, males are more likely to consider and ask for regrades compared to females (except for those with 1 class).

>>>>

---
title: "Gender Dynamics in Academia: Analyzing Regrade Requests and Course Load Trends, 2010-2016"
subtitle: "A replication of Li and Zahar;"
author: Faiza Imam, Quang Mai & Catherine Punnoose 
thanks: "Code and data are available at: https://github.com/ponolite/gender_grade.git, DOI: 10.1257/pol.20210053"
date: today
date-format: long
abstract: "Academia is a complex ecosystem that feeds off a network of social, cultural and innovative influences which often, stem beyond societal norms. This paper replicates the gender implications regarding results in college students and explores potential fluctuations in request patterns over a semester by specifically analyzing the number of classes taken by students and their willingness to submit a grade request throughout the semester. Our results show that there is a trend for female students to submit regrade requests while taking fewer courses compared to a higher course load. Female students experienced grade increases (3%) compared to their male counterparts. We call for further investigation around this topic to understand gender disparities within the world of academia. "
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

Suceedingly, @fig-RegradeByClass shows the averaged distribution of the number of classes in which students are considered for regrades by gender. Observable in the graph, there is only data available on students who considered regrades in ‘0 class’ to ‘5 classes or more’ ([@fig-RegradeByClass]). Therefore, with the number of classes limited to 5, it’s more than likely that surveys understate the regraded data [@GenderDiff]. Observably, with no or 0 classes, the majority of students didn’t consider regrade requests, with females upholding 41.2 % while males upholding 39.3%, making it a 1.9% difference. This trend of females considering for regrades is higher than males when the class number is lower, where at 1 class, a whopping 30.4% of females are considered for regrades in contrast to a meagre 22.7% of males. This translates to a huge margin of 7.7% between the two genders. However, as the number of classes extended above 1, or from 2 to 5 or more classes, more males considered asking for a regrade. For instance, at 3 classes, 8.9% of males considered for regrades as opposed to 7.1% of females; at 4 classes, 3.3% of males considered for regrades compared to 2% of females and finally, at 5 classes or more, a great 5.2% of males considered for regrades compared to a small 2.1% females. Statistically then, while the difference is negligible in some categories of class number, males are more likely to consider and ask for regrades compared to females (except for those with 1 class).
